\documentclass{article}

\begin{document}

\title{\bf Rules of Procedure for TU Delft SIAM Student Chapter}
\maketitle

This Rules of Procedure (hereinafter called ``Rules'') apply to the SIAM Student Chapter called ``TU Delft Chapter of SIAM''.
The Student Chapter to which these Rules apply is formed by the Society for Industrial and Applied Mathematics and shall operate within the Bylaws of the parent organization. The SIAM bylaws specify how Student Chapters are formed; see the SIAM bylaws for details. The Chapter shall not affiliate with any other organization without first obtaining the written approval of SIAM. Provisions for SIAM Student (University) Chapters are contained in the SIAM Bylaws and are included in these Rules. No provisions of these rules shall be construed so as to contradict the Bylaws of SIAM.
 
\section*{ARTICLE I: PURPOSE}
The objectives of SIAM, as established in the Certificate of Incorporation, are:
\begin{itemize}
\item To further the application of mathematics to industry and science.
\item To promote basic research in mathematics leading to new methods and techniques useful to industry and science.
\item To provide media for the exchange of information and ideas between mathematicians and other technical and scientific personnel.
\end{itemize}
Purposes of the Student Chapter shall be consistent with the objectives of SIAM.  
The Student Chapter at TU Delft aims for activities organized by the PhD students, which connect the different departments and links to industry.
 
\section*{ARTICLE II: ACTIVITIES}
\begin{itemize}
\item Organize Scientific talks about Applied Mathematics and Computer Science given by students and faculty members.
\item Organize lectures about scientific software and computer tools.
\item Promote the SIAM events and activities in internet using social networks.
\item Organize social activities for members of the Chapter.
\item Participate in student day and poster session at SIAM Annual Meeting.
\item Sponsor lectures by guest speakers.
\item The Student Chapter annually awards a price for the best thesis at Applied Mathematics.
\end{itemize}
\section*{ARTICLE III: INSTITUTION SERVED}
Student chapter members will be recruited at TU Delft, both from Applied Mathematics and connected fields.
 
\section*{ARTICLE IV: MEMBERSHIP}
\subsection*{Section 1} Any student engaged or interested in mathematics or computing and their applications shall be eligible for membership in this Chapter.  SIAM encourages chapters to be interdisciplinary, including student members from multiple departments. The Chapter organizers encourage all members to become Regular Members or Student Members in SIAM. 
\subsection*{Section 2} The Chapter differentiate three types of memberships, which are all free. Full members of the Chapter are PhD students, staff members can become senior members of the Chapter. MSc students can temporarily be added to the Chapter as junior members. Membership should be declared to the Board.
\subsection*{Section 3} Chapter members shall have the privileges of SIAM membership only if they are regular or student members of SIAM. Full members have active and passive voting rights for the Chapter Board. The Board is responsible for all activities of the Chapter. Senior and junior members are allowed to join all activities and may suggest events.
\subsection*{Section 4} All members of the chapter who are students enrolled in the sponsoring institution(s) are eligible for free student memberships in SIAM. Chapters shall encourage their members to join SIAM either online, by submitting printed membership applications, or  by submitting a list of its student members to SIAM so that complimentary student membership in SIAM can be processed. Free student memberships may be renewed every year that the student remains a student member of the chapter. The Board is responsible to keep track of a member's list. 
\subsection*{Section 5} Termination of student membership will take place upon graduation or withdrawal from the university or upon failure to pay dues.
 
\section*{ARTICLE V: SPONSORSHIP}
\subsection*{Section 1} The Sponsor is TU Delft. The university will provide rooms and equipment for all activities.
\subsection*{Section 2} The Sponsor of the Chapter shall appoint a Faculty Advisor for the Chapter. The Advisor must be a member in good standing with SIAM. In the event said Advisor relinquishes his/her position, the Sponsor shall appoint a new Advisor.  The responsibilities, rights and duties of the Faculty Advisor shall be those normally assigned to the Faculty Advisor of student organizations of the Sponsor, but in addition, the Faculty Advisor is expected to take leading role in the development of the Chapter activities consistent with the objectives of SIAM.

\subsection*{Section 3} The Board is responsible for the content of all activities of the Chapter. The role of the Faculty Advisor is to have a long-term view of the Chapter.
 
\section*{ARTICLE VI: OFFICERS}
\subsection*{Section 1} The Chapter shall have a President, a Vice-President, a Secretary, a Treasurer and a Webmaster. The Treasurer and Secretary can be one person. Officers shall be chosen from Student Members of the Chapter and must be Student Members in good standing with SIAM. The members of the Board are elected for one academic year by the full members of the Chapter. The first Board will be installed by the Faculty Advisor for the academic year 2014 - 2015.
\subsection*{Section 2} The President shall preside at the meetings of the Chapter (and the Chapter Executive Committee (see Article VII below)).  In the absence of the President, the Vice-President shall assume the duties of the President.  In the absence of the latter, the Secretary shall assume said duties. In particular, the Vice-President is responsible for promoting the Chapter.
\subsection*{Section 3} The Secretary shall keep a record of the affairs of the Chapter, handle correspondence, and submit an annual report of Chapter activities to the Secretary of SIAM, which report shall be suitable for publication in SIAM News or its equivalent.
\subsection*{Section 4} The Treasurer shall receive and take custody of Chapter funds, and shall submit an annual Treasurer's Report and other financial reports, as requested, to the Treasurer of SIAM.  The annual Treasurer's Report shall be prepared as of the end of the academic year and shall be transmitted to the Treasurer of SIAM by no later than 30 days following the end of the academic year.
\subsection*{Section 5} Terms of Chapter officers cannot exceed two years, but re-election of an officer after one year for an additional term should be permissible.

\section*{ARTICLE VII: MEETINGS}
\subsection*{Section 1} There shall be at least six meetings per year. Meetings can be related to mathematics, industry, implementation, or social events. Although the Board is responsible for the meeting topics, every member can suggest and organize Chapter events. Lectures are open to everyone, but only members can attend annual meetings and company visits.
\subsection*{Section 2} The Chapter shall conduct a business meeting once per year during the month of July.  Other business meetings may be called by the President or the Treasurer on two weeks notice.
\subsection*{Section 3} At the annual meeting, we intend to elect a board for the next academic year.
 
\section*{ARTICLE VIII: CHAPTER FUNDS}
\subsection*{Section 1} The Chapter may levy dues, voluntary or otherwise, collect registration fees for Chapter meetings, and otherwise raise funds in any lawful manner consistent with these Rules and the Bylaws and Certificate of Incorporation of SIAM.  
\subsection*{Section 2} Chapter membership is free. Even when activities of the Chapter may require a registration fee, this does not affect the membership status.
\subsection*{Section 3} The Chapter shall deposit all unused funds to which it has legal title in excess of \$200 in an insured savings account, unless current operating commitments are in excess of that amount or unless the Chapter Treasurer obtains a written authorization from the SIAM Treasurer.
\subsection*{Section 4} The Treasurer shall maintain books of account that show income and expense items for all activities and balances for all accounts of the Chapter.
\subsection*{Section 5} The Chapter may request a grant or loan from the Treasurer of SIAM under the provision of Article XIi, Chapter 8 of the Bylaws of SIAM.  Such requests shall be made by submission of ``Request for Funding'' form to SIAM and include a current financial statement for the Chapter and a proposed budget for the requested funds.
\subsection*{Section 6} Other than seeking funds from the sponsoring institutions of the chapter, no officers or member of the Chapter may apply for a grant to support the Chapter activities or enter into any contract to support such activities or provide services, without approval of the President and the Treasurer of SIAM or the Executive Director acting on behalf of the Treasurer.
 
\section*{ARTICLE IX: AMENDMENTS}
\subsection*{Section 1} These Rules may be altered or amended with the approval of the SIAM Board of Trustees.  Submission to the board of proposal alterations or amendments shall be made only after approval by majority vote of members of the Chapter present (or represented by proxy) at a scheduled meeting.
 
\section*{ARTICLE X: TERMINATION OF THE CHAPTER}
\subsection*{Section 1} A Chapter may terminate itself by the unanimous vote of the members of the Chapter present (or represented by proxy) at a scheduled meeting, provided that notice of the proposed termination and the meeting at which it is to be considered has been given to all Chapter members at least 30 days in advance.
\subsection*{Section 2} A Chapter may be terminated by the board if there has been no Chapter activity for one year.
\subsection*{Section 3} In the event a Chapter terminates, the funds to which it has legal title shall revert to the account of SIAM.
\end{document}